\sysfull

### 2018-04-10 paper/intro.tex
random

We evaluated \sys end-to-end on a real energy-harvesting device~\cite{wisp} running existing benchmarks ~\cite{chain} and new programs. A comparison to a state-of-the-art task-based system~\cite{chain} showed that \sys recovers
performance on conservative task decompositions missed by systems with static decomposition.
%
%and can flexibly target a variety of platforms without rewriting code.
%
%\todo{Provide concrete numeric results supporting this claim}{Amjad/Przemek}

>>>>

We evaluated \sys end-to-end on a real energy-harvesting device~\cite{wisp} running existing benchmarks ~\cite{chain} and new programs. A comparison to a state-of-the-art task-based system~\cite{aplaca} showed that \sys recovers
performance on conservative task decompositions missed by systems with static decomposition.
%
%and can flexibly target a variety of platforms without rewriting code.
%
%\todo{Provide concrete numeric results supporting this claim}{Amjad/Przemek}

### 2018-04-10 paper/paper.tex
random

\acmConference[Submitted to OOPSLA'18]{ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 18--22, 2018}{Philadelphia, PA, USA}

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Adaptive Task Coalescing $\ldots$}
\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

\input{background}

\section{\sys: System Overview}
\label{sec:overall_system}

\input{systemdescription}

\section{Task Coalescing}
\label{sec:task_coalescing}

\input{coalescing}
% \input{newCoalescing}

\section{Memory Virtualization}
\label{sec:memory_virtulaization}

\input{paging}

>>>>

\acmConference[Submitted to PLDI'18]{ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 18--22, 2018}{Philadelphia, PA, USA}

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{ROO\xspace}
%\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Adaptive Intermittent Execution Model $\ldots$}
%\newcommand{\sysmed}{\sys: Adaptive Task Coalescing $\ldots$}
%\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
\newcommand{\sysfull}{\sys: Adaptive Intermittent Execution Model for Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

\input{background}
\section{\sys: Adaptive Intermittent Execution Model}
\label{sec:adaptiveExecModel}
\input{adaptiveModel.tex}

\subsection{\sys: Coalescing}
\label{sec:implementation}
\input{newCoalescing}
\input{coalescing}

\subsection{\sys: Memory Virtualization}
\label{sec:memory_virtulaization}
\input{paging}

\section{\sys Implementation}
\label{sec:implementation}
\input{systemdescription}
